The \dealii Library, Version 9.2

### 2020-05-28 9.2/paper.tex
Resolve another todo.

The major changes of this release are:
%
\begin{itemize}
\item xy \todo[inline]{Update once we have the subsections in Section 2;
  provide cross-references to each of these subsections}
%   \item Improved support for automatic differentiation (see
%     Section~\ref{subsec:ad}),
\end{itemize}
%
These major changes are discussed in detail in Section~\ref{sec:major}. There
are a number of other noteworthy changes in the current \dealii{} release
that we briefly outline in the remainder of this section:
%
\begin{itemize}
\item \dealii{} had decent support for solving complex-valued problems
  for a while already
  (e.g., ones in quantum mechanics -- like the equation used in the
  \texttt{step-58} tutorial program covered below -- or for
  time-harmonic problems). However, there were two
  areas in which support was missing. First, the UMFPACK direct solver
  packaged with \dealii{} did not support solving complex-valued
  linear problems. This has now been addressed: UMFPACK actually can
  solve such systems, we just needed to write the appropriate
  interfaces. Second, the \texttt{DataOut} class that is responsible
  for converting nodal data into information that can then be written
  into files for visualization did not know how to deal with vector-
  and tensor-valued fields whose components are complex numbers. An
  example for this is to solve the time-harmonic version of the
  Maxwell equations that has the electric and magnetic fields as
  solution. This, too, has been addressed in this release.
\item The new \texttt{DiscreteTime} class provides a more
  consistent, more readable, and less error-prone approach to control
  time-stepping algorithms within time-dependent simulations.
  The interface of this class is designed to be minimal
  to enforce a number of important programming invariants, reducing
  the possibility of mistakes in the user code.
  An example is that \texttt{DiscreteTime} ensures that the final time step ends
  precisely on a predefined end time, automatically
  lengthening or shortening to final time step.
\item z \todo[inline]{What else? Maybe mention the updated step-12?}
\end{itemize}
%
The changelog lists more than 240 other
features and bugfixes.

>>>>

The major changes of this release are:
%
\begin{itemize}
\item xy \todo[inline]{Update once we have the subsections in Section 2;
  provide cross-references to each of these subsections}
%   \item Improved support for automatic differentiation (see
%     Section~\ref{subsec:ad}),
\end{itemize}
%
These major changes are discussed in detail in Section~\ref{sec:major}. There
are a number of other noteworthy changes in the current \dealii{} release
that we briefly outline in the remainder of this section:
%
\begin{itemize}
\item \dealii{} had decent support for solving complex-valued problems
  for a while already
  (e.g., ones in quantum mechanics -- like the equation used in the
  \texttt{step-58} tutorial program covered below -- or for
  time-harmonic problems). However, there were two
  areas in which support was missing. First, the UMFPACK direct solver
  packaged with \dealii{} did not support solving complex-valued
  linear problems. This has now been addressed: UMFPACK actually can
  solve such systems, we just needed to write the appropriate
  interfaces. Second, the \texttt{DataOut} class that is responsible
  for converting nodal data into information that can then be written
  into files for visualization did not know how to deal with vector-
  and tensor-valued fields whose components are complex numbers. An
  example for this is to solve the time-harmonic version of the
  Maxwell equations that has the electric and magnetic fields as
  solution. This, too, has been addressed in this release.
\item The new \texttt{DiscreteTime} class provides a more
  consistent, more readable, and less error-prone approach to control
  time-stepping algorithms within time-dependent simulations.
  The interface of this class is designed to be minimal
  to enforce a number of important programming invariants, reducing
  the possibility of mistakes in the user code.
  An example is that \texttt{DiscreteTime} ensures that the final time step ends
  precisely on a predefined end time, automatically
  lengthening or shortening to final time step.
\item A key component of \dealii{} are the \texttt{FEValues} and
  \texttt{FEFaceValues} classes that evaluate finite element functions
  at quadrature points located on cells and faces of a cell,
  respectively~\cite{BangerthHartmannKanschat2007}. This release now
  contains a class \texttt{FEInterfaceValues} that considers the
  restriction of the shape functions from \textit{both} sides of a face and
  allows evaluating jumps and averages of shape functions along this
  face. These are common components of the bilinear forms of
  discontinuous Galerkin schemes (as well as schemes for fourth-order
  equations, see the discussion of \texttt{step-47} below) and greatly
  simplify the implementation of these methods.
\end{itemize}
%
The changelog lists more than 240 other
features and bugfixes.
